\documentclass[14pt]{article}
\openup 1em

\title{Narrative}
\date{2017-03--5}
\author{Lucas Arias\
        \and
        Chuck Coleman\
        \and
        Nora Cook\
        \and
        TJ Mitchell
        }
\begin{document}
        \maketitle
        \newpage

        Munchies Inc. is a business dedicated to making review sites for small
        businesses. We will also be developing services for file storage and email 
        that small businesses can take advantage of. These services will allow 
        small business to be more efficient without the need for a costly in-house
        solution.\\

        The main focus of Munchies Inc. is our website Welp. This website will
        act as a service for Alfred residents to find information about local 
        businesses. It will include menus and prices for restaurants and will 
        also allow reviews for registered users. The website will help locals 
        become more aware of local businesses and boost their business. It will 
        also empower the consumer by giving them more information products they
        may want to buy.\\

        Along with a public website, we will also offer file storage allowing
        businesses to save money by using less paper. It will also help 
        organization as there will be no papers to lose.\\

        We will also have email services available. Having a private email service
        will help businesses keep information secure and more private rather than
        using a public service such as gmail.\\

\end{document}
